---
output: github_document
editor_options: 
  chunk_output_type: console
markdown: 
    wrap: 72
execute:
  echo: false
bibliography: references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE,
  fig.retina = 2,
  fig.align = 'center'
)

library(tidyverse)
library(biogasoutcomesmalawi)

```

# biogasoutcomesmalawi

<!-- badges: start -->

[![R-CMD-check](https://github.com/Global-Health-Engineering/biogasoutcomes/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Global-Health-Engineering/biogasoutcomes/actions/workflows/R-CMD-check.yaml)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.8289621.svg)](https://doi.org/10.5281/zenodo.8289621)
[![License: CC BY 4.0](https://img.shields.io/badge/License-CC_BY_4.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

<!-- badges: end -->

The goal of biogasoutcomesmalawi is to provide a qualitative dataset in a table format. The dataset consists of 61 semi-structured interviews with biogas owners in the Southern Region of Malawi. Interviews were conducted over multiple visits to sites over the course of a two-year period between June 2021 and October 2022.

## Installation

You can install the development version of biogasoutcomesmalawi from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("openwashdata/biogasoutcomesmalawi")
```

Alternatively, you can download the individual datasets as a CSV or XLSX file from the table below. 

```{r, echo=FALSE}

extdata_path <- "https://github.com/openwashdata/biogasoutcomesmalawi/raw/main/inst/extdata/"

read_csv("data-raw/dictionary.csv") |> 
  distinct(file_name) |> 
  mutate(file_name = str_remove(file_name, ".rda")) |> 
  rename(dataset = file_name) |> 
  mutate(
    CSV = paste0("[Download CSV](", extdata_path, dataset, ".csv)"),
    XLSX = paste0("[Download XLSX](", extdata_path, dataset, ".xlsx)")
  ) |> 
  knitr::kable()

```

The original transcripts in .docx file format and converted to .md (markdown) file format are can be accessed from: https://github.com/openwashdata/biogasoutcomesmalawi/tree/main/data-raw

## Description

Within Sub-Saharan Africa, biogas projects have seen significant investment, but with a chequered record of success. Although the potential for biogas is well covered in contemporary literature, biogas owners, and their relationship to project outcomes, remains underexplored. Focusing on southern Malawi, and combining qualitative interviews with owners, with on-site socio-technical investigation, the purpose of this research was to explore the role of individual owners in contributing to project success or failure.

This dataset represents a complete sample of biogas installations (at the time of the research) located within Malawi's Southern Region. The dataset consists of 61 semi-structured interviews with biogas owners, conducted over multiple visits to sites over the course of a two-year period between June 2021 and October 2022. This data was supplemented by additional data collection, which is not include in this published dataset, consisting of more than 20 unstructured interviews, field notes, participatory observation, detailed socio-technical analysis of each digester system, and countless impromptu conversations, Whatsapp discussions, and phone calls.

Sites were identified through an initial scoping phase of the study, which involved an exhaustive search for biogas sites from within secondary documents and from consultations with key stakeholders within the country, including biogas installers and representatives from the Malawi Energy Regulatory Authority. Inclusion for participation centred on the ownership of a biogas system. Only one interview per biogas site was conducted. In sites with more than one relevant stakeholder/owner, all stakeholders willing to be interviewed were included in the interview.

Interviews were conducted in the local language (Chichewa), audio recorded, and transcribed into English. Participation was voluntary and could be withdrawn at any time. Respondents providing written, informed consent, and responses were recorded anonymously. This study received ethical approval from National Committee on Research in the Social Sciences and Humanities, Protocol No. P.03/21/560.

## Related publications

This data was used in a publication currently under review:

Kalina, M., Ogwang, J.O., Kwangulero, J., and E. Tilley (2023) Uncovering biogas outcomes: tales of hubris, hope, and failure from southern Malawi. Natural Resources Forum. 

This data was used in @kalina2022:

<div id="refs"></div>
<br>

## List of documentation files

In addition to the data from the interviews, the following files are provided with the data package. These files can be accessed via GitHub, as they are contained in:

<https://github.com/openwashdata/biogasoutcomesmalawi/tree/main/inst/extdata>

### information-letter_chichewa.docx

Description: Information letter in Chichewa. This letter was read to all participants prior to each interview. It describes the purpose and nature of the research, as well as expectations and protections for respondents.

### information-letter_english.docx

Description: Information letter translated into English. This letter was read to all participants prior to each interview. It describes the purpose and nature of the research, as well as expectations and protections for respondents.

### informed-consent-form_chichewa.docx

Description: Informed consent form in Chichewa. Written informed consent was sought from all respondents. Signed consent forms are being securely stored in Blantyre, Malawi until 2027 when they will be destroyed.

### informed-consent-form_english.docx

Description: Informed consent form translated into English. Written informed consent was sought from all respondents. Signed consent forms are being securely stored in Blantyre, Malawi until 2027 when they will be destroyed.

### interview-schedule_chichewa.docx

Description: Utilised interview schedule in Chichewa. Interviews were loosely structured, with a narrative focus, to allow the respondents to tell their stories, and share their experiences with their digesters. Interviews also included substantial participatory elements, with owners, particularly at the households, allowing the researchers to join them throughout their daily routines, including their daily regimen of feeding, maintenance, and use of the biodigester system, when applicable.

### interview-schedule_english.docx

Description: Utilised interview schedule translated into English. Interviews were loosely structured, with a narrative focus, to allow the respondents to tell their stories, and share their experiences with their digesters. Interviews also included substantial participatory elements, with owners, particularly at the households, allowing the researchers to join them throughout their daily routines, including their daily regimen of feeding, maintenance, and use of the biodigester system, when applicable.

### site-inspection-checklist.docx

Description: Socio-technical site analysis of each biogas plant was conducted using a checklist adapted from troubleshooting guidelines published by AGAMA Biogas (Ayres, 2018). Sites in operation were tested on a number of criteria including: gas pressure, flame colour, and pH (in the reactive chamber and of the digestate).

## License

Data are available as [CC-BY](https://github.com/openwashdata/biogasoutcomesmalawi/blob/main/LICENSE.md).

## Citation

Please cite using:

```{r}
citation("biogasoutcomesmalawi")
```
